---
title: "Lab 1 - Data visualization"
author: "Karina Marinovich"
format: pdf
editor: visual
---

## Load Packages

```{r}
#| label: load-packages
#| message: false

library(tidyverse)
library(viridis)
```

## Exercise 1

(Type your answer to Exercise 1 here. Add code chunks as needed. Don't forget to label your code chunk. Do not use spaces in code chunk labels.)

```{r ex-1}
#| label: histogram-population-density 
ggplot(midwest,
       aes(x = popdensity)) +
  geom_histogram(binwidth = 10000) + labs(x = "Population Density", y = "County", title = "Population Density of Midwest Counties")
```
The shape of the distribution of Population Density of Midwest Counties is asymmetrical, skewed right. 
There appears to be an outlier when the population density is around 90,000
## Exercise 2
```{r ex-2}
#| label: scatterplot_percollege
ggplot(midwest, aes(x = percollege, y = percbelowpoverty, color = state)) + geom_point() + labs(x= "Percent of People Who Attended College", y = "Percent of People Below Poverty", color = "State", title = "Attending College versus Poverty Rates") + scale_fill_viridis()

```

(Type your answer to Exercise 2 here. Add code chunks as needed. Don't forget to label your code chunk. Do not use spaces in code chunk labels.)

## Exercise 3

(Type your answer to Exercise 3 here. Add code chunks as needed. Don't forget to label your code chunk. Do not use spaces in code chunk labels.)

## Exercise 4

## Exercise 5

## Exercise 6

## Exercise 7
